Slides for Social Network Paper

### 2025-04-15 ProjectBlog/paper2/Paper 2 Slides 2/p2literature.qmd
paper 2
paper 2 by break

@@

<iframe src="pdfs/Social_Network_Paper_Slides.pdf" style="width:100%; height:1500px;" frameborder="0">

@@

>>>>

# Mechanism

![](images/clipboard-4127087002.png){fig-align="center"}

![](images/clipboard-2231454442.png){fig-align="center"}

# Restults with Comm Vs NoComm Screen Time

![](images/clipboard-1110454764.png){fig-align="center"}

![](images/clipboard-1333816286.png)

@@

<iframe src="pdfs/Social_Network_Paper_Slides___CHITA.pdf" style="width:100%; height:1500px;" frameborder="0">

@@

## Economic Analysis and Policy

![](images/Camera_XHS_17447327922881040g2sg312icvo3s0c7g48uveq05df6k24ft9o8.jpg){fig-align="center"}
